\section {The shmUtil 1.0.0 Library} \subsection {shmUtil.h} \begin{description} \item[\sc use:] \emph{\#include ``shmUtil.h''} \item[\sc description:] this file contains all common code required by the functions needed to build the static and dynamic shmUtil libraries. These libraries abstract the shared memory interface to the system. \item[\sc argument(s):] not applicable \item[\sc return(s):] not applicable \item[\sc last modified:] Monday, 4 November 2002 \end{description}
\subsection {shmUtilAttach} \begin{description} \item[\sc use:] \emph{void $\star$shmUtilAttach(long $\star$istat, char $\star$resp, char $\star$libName, int $\star$create, int size);} \item[\sc description:] this function initializes the shared memory segment. The inherited status is updated. \item[\sc argument(s):] \begin{description} \item[\ ] \ \item[\emph{long $\star$istat}] the inherited status value. \item[\emph{char $\star$resp}] a user supplied buffer for message strings. \item[\emph{char $\star$libName}] the library name. \item[\emph{int $\star$create}] TRUE if we need to create the segment first (returns shmid). \item[\emph{int size}] the size of the desired segment. \end{description} \item[\sc return(s):] pointer to memory address or (void $\star$) NULL. \item[\sc last modified:] Wednesday, 12 March 2003 \item[\sc author(s):] Nick Buchholz (ncb), Phil Daly (pnd) \item[\sc license:] (c) 2002 AURA Inc. All rights reserved, Released under the GPL. \end{description}
\subsection {shmUtilDetach} \begin{description} \item[\sc use:] \emph{void shmUtilDetach(long $\star$istat, char $\star$resp, char $\star$libName, void $\star$address );} \item[\sc description:] this function detaches from the shared memory segment for global library variables. A flag indicates that the memory should also be destroyed. The inherited status is updated and returned along with a message response. \item[\sc argument(s):] \begin{description} \item[\ ] \ \item[\emph{long $\star$istat}] the inherited status value. \item[\emph{char $\star$resp}] a user supplied buffer for message strings. \item[\emph{char $\star$libName}] the library name. \item[\emph{void $\star$address}] the address of the segment to detach from. \end{description} \item[\sc return(s):] void \item[\sc last modified:] Thursday, 21 November 2002 \item[\sc author(s):] Phil Daly (pnd), Nick Buchholz (ncb) \item[\sc license:] (c) 2002 AURA Inc. All rights reserved. Released under the GPL. \end{description}
\subsection {shmUtilInit} \begin{description} \item[\sc use:] \emph{key\_t shmUtilInit(long $\star$istat, char $\star$resp, char $\star$libName, int $\star$create);} \item[\sc description:] this function initializes the shared memory segment file lock. The inherited status is updated. \item[\sc argument(s):] \begin{description} \item[\ ] \ \item[\emph{long $\star$istat}] the inherited status value. \item[\emph{char $\star$resp}] a user supplied buffer for message strings. \item[\emph{char $\star$libName}] the library name. \item[\emph{int $\star$create}] TRUE if we need to create the segment first (returns shmid). \end{description} \item[\sc return(s):] a key\_t related to the lock file to be used in creating the shared memory \item[\sc last modified:] Monday, 12 March 2003 \item[\sc author(s):] Nick Buchholz (ncb), Phil Daly (pnd) \item[\sc license:] (c) 2002 AURA Inc. All rights reserved, Released under the GPL. \end{description}
\subsection {shmUtilSize} \begin{description} \item[\sc use:] \emph{u\_long shmUtilSize(long $\star$istat, char $\star$resp, u\_long $\star$inSize, u\_long inUnit);} \item[\sc description:] this function resizes inSize so that it is an exact multiple of of inUnit. It is used to ensure boundary integrity prior to memory allocation. The inherited status is updated. \item[\sc argument(s):] \begin{description} \item[\ ] \ \item[\emph{long $\star$istat}] the inherited status value. \item[\emph{char $\star$resp}] a user supplied buffer for message strings. \item[\emph{u\_long $\star$inSize}] input size (modified on return). \item[\emph{u\_long inUnit}] the base unit for re-sizing. \end{description} \item[\sc return(s):] number of elements in new inSize. \item[\sc last modified:] Monday, 4 November 2002 \item[\sc author(s):] Phil Daly (pnd) \item[\sc license:] (c) 2002 AURA Inc. All rights reserved, Released under the GPL. \end{description}
\subsection {shmUtilUninit} \begin{description} \item[\sc use:] \emph{void shmUtilUninit(long $\star$istat, char $\star$resp, char $\star$libName);} \item[\sc description:] this function un-initializes the shared memory segment. The inherited status is updated. \item[\sc argument(s):] \begin{description} \item[\ ] \ \item[\emph{long $\star$istat}] the inherited status value. \item[\emph{char $\star$resp}] a user supplied buffer for message strings. \item[\emph{char $\star$libName}] the library name. \end{description} \item[\sc return(s):] void. \item[\sc last modified:] Monday, 4 November 2002 \item[\sc author(s):] Nick Buchholz (ncb), Phil Daly (pnd) \item[\sc license:] (c) 2002 AURA Inc. All rights reserved, Released under the GPL. \end{description}
