\subsection {dhsUtilAux} \begin{description} \item[\sc use:] \emph{Not Applicable} \item[\sc description:] This module declares a single global variable a shared memory structure pointer. This variable is used to contain the pointer to the shared memory used by the library routines for global info \item[\sc argument(s):] None \item[\sc return(s):] None \item[\sc last modified:] Wednesday, 21 January 2003 \end{description}
\subsection {dhsUtilCloseConnect} \begin{description} \item[\sc use:] \emph{void dhsUtilCloseConnect(long $\star$istat, char $\star$resp, dhsHandle dhsID);} \item[\sc description:] close a connection to the DHS. \item[\sc argument(s):] \begin{description} \item[\ ] \ \item[\emph{long $\star$istat}] the inherited status value. \item[\emph{char $\star$resp}] a user supplied buffer for message strings. \item[\emph{dhsHandle dhsID}] dhs handle. \end{description} \item[\sc return(s):] void. \item[\sc author(s):] Peter Ruckle, Phil Daly \item[\sc last modified:] \item[\sc license:] (c) 2004 AURA Inc. All rights reserved. Released under the GPL. \end{description}
\subsection {dhsUtilCloseExp} \begin{description} \item[\sc use:] \emph{void dhsUtilCloseExp(long $\star$istat, char $\star$resp, dhsHandle dhsID, double expID);} \item[\sc description:] close an exposure connection to the DHS. \item[\sc argument(s):] \begin{description} \item[\ ] \ \item[\emph{long $\star$istat}] the inherited status value. \item[\emph{char $\star$resp}] a user supplied buffer for message strings. \item[\emph{dhsHandle dhsID}] dhs handle. \item[\emph{double expID}] exposure identifier. \end{description} \item[\sc return(s):] void. \item[\sc author(s):] Peter Ruckle, Phil Daly \item[\sc last modified:] \item[\sc license:] (c) 2004 AURA Inc. All rights reserved. Released under the GPL. \end{description}
\subsection {dhsUtilIOCtl} \begin{description} \item[\sc use:] \emph{void dhsUtilIOCtl(long $\star$istat, char $\star$resp, dhsHandle dhsID, ulong ioctlFunction, double $\star$expID, char $\star$obsetID, ...);} \item[\sc description:] send ioctl data to the DHS. \item[\sc argument(s):] \begin{description} \item[\ ] \ \item[\emph{long $\star$istat}] the inherited status value. \item[\emph{char $\star$resp}] a user supplied buffer for message strings. \item[\emph{dhsHandle dhsID}] dhs handle. \item[\emph{ulong ioctlFunction}] ioctl function. \item[\emph{double $\star$expID}] exposure identifier. \item[\emph{char $\star$obsetID}] observation set identifier. \end{description} \item[\sc return(s):] void. \item[\sc author(s):] Peter Ruckle, Phil Daly \item[\sc last modified:] \item[\sc license:] (c) 2004 AURA Inc. All rights reserved. Released under the GPL. \end{description}
\subsection {dhsUtilOpenConnect} \begin{description} \item[\sc use:] \emph{void dhsUtilOpenConnect(long $\star$istat, char $\star$resp, dhsHandle $\star$dhsID, ulong whoami, fpConfig\_t $\star$cfg);} \item[\sc description:] open a connection to the DHS. \item[\sc argument(s):] \begin{description} \item[\ ] \ \item[\emph{long $\star$istat}] the inherited status value. \item[\emph{char $\star$resp}] a user supplied buffer for message strings. \item[\emph{dhsHandle $\star$dhsID}] returned dhs handle. \item[\emph{ulong whoami}] identifier for NOCS or MSL or other system making the call. \item[\emph{fpConfig\_t $\star$cfg}] focal plane configuration. \end{description} \item[\sc return(s):] void. \item[\sc author(s):] Peter Ruckle, Phil Daly \item[\sc last modified:] \item[\sc license:] (c) 2004 AURA Inc. All rights reserved. Released under the GPL. \end{description}
\subsection {dhsUtilOpenExp} \begin{description} \item[\sc use:] \emph{void dhsUtilOpenExp(long $\star$istat, char $\star$resp, dhsHandle dhsID, fpConfig\_t $\star$cfg, double $\star$expID, char $\star$obsetID);} \item[\sc description:] open an exposure connection to the DHS. \item[\sc argument(s):] \begin{description} \item[\ ] \ \item[\emph{long $\star$istat}] the inherited status value. \item[\emph{char $\star$resp}] a user supplied buffer for message strings. \item[\emph{dhsHandle dhsID}] dhs handle. \item[\emph{fpConfig\_t $\star$cfg}] focal plane configuration. \item[\emph{double $\star$expID}] exposure identifier. \item[\emph{char $\star$obsetID}] observation set identifier. \end{description} \item[\sc return(s):] void. \item[\sc author(s):] Peter Ruckle, Phil Daly \item[\sc last modified:] \item[\sc license:] (c) 2004 AURA Inc. All rights reserved. Released under the GPL. \end{description}
\subsection {dhsUtilReadImage} \begin{description} \item[\sc use:] \emph{void dhsUtilReadImage(long $\star$istat, char $\star$resp, dhsHandle dhsID);} \item[\sc description:] close a connection to the DHS. \item[\sc argument(s):] \begin{description} \item[\ ] \ \item[\emph{long $\star$istat}] the inherited status value. \item[\emph{char $\star$resp}] a user supplied buffer for message strings. \item[\emph{dhsHandle dhsID}] dhs handle. \end{description} \item[\sc return(s):] void. \item[\sc author(s):] Peter Ruckle, Phil Daly \item[\sc last modified:] \item[\sc license:] (c) 2004 AURA Inc. All rights reserved. Released under the GPL. \end{description}
\subsection {dhsUtilSendMetaData} \begin{description} \item[\sc use:] \emph{void dhsUtilSendMetaData(long $\star$istat, char $\star$resp, dhsHandle dhsID, void $\star$blkAddr, size\_t blkSize, mdConfig\_t $\star$cfg, double $\star$expID, char $\star$obsetID);} \item[\sc description:] send meta data to the DHS. \item[\sc argument(s):] \begin{description} \item[\ ] \ \item[\emph{long $\star$istat}] the inherited status value. \item[\emph{char $\star$resp}] a user supplied buffer for message strings. \item[\emph{dhsHandle dhsID}] dhs handle. \item[\emph{void $\star$blkAddr}] address of data block. \item[\emph{size\_t $\star$blkSize}] size of data block. \item[\emph{mdConfig\_t $\star$cfg}] meta data configuration. \item[\emph{double $\star$expID}] exposure identifier. \item[\emph{char $\star$obsetID}] observation set identifier. \end{description} \item[\sc return(s):] void. \item[\sc author(s):] Peter Ruckle, Phil Daly \item[\sc last modified:] \item[\sc license:] (c) 2004 AURA Inc. All rights reserved. Released under the GPL. \end{description}
\subsection {dhsUtilSendPixelData} \begin{description} \item[\sc use:] \emph{void dhsUtilSendPixelData(long $\star$istat, char $\star$resp, dhsHandle dhsID, void $\star$pxlAddr, size\_t pxlSize, fpConfig\_t $\star$cfg, double $\star$expID, char $\star$obsetID);} \item[\sc description:] send pixel data to the DHS. \item[\sc argument(s):] \begin{description} \item[\ ] \ \item[\emph{long $\star$istat}] the inherited status value. \item[\emph{char $\star$resp}] a user supplied buffer for message strings. \item[\emph{dhsHandle dhsID}] dhs handle. \item[\emph{void $\star$pxlAddr}] address of data block. \item[\emph{size\_t $\star$pxlSize}] size of data block. \item[\emph{fpConfig\_t $\star$cfg}] pixel data configuration. \item[\emph{double $\star$expID}] exposure identifier. \item[\emph{char $\star$obsetID}] observation set identifier. \end{description} \item[\sc return(s):] void. \item[\sc author(s):] Peter Ruckle, Phil Daly \item[\sc last modified:] \item[\sc license:] (c) 2004 AURA Inc. All rights reserved. Released under the GPL. \end{description}
\subsection {dhsUtilSysClose} \begin{description} \item[\sc use:] \emph{void dhsUtilSysClose(long $\star$istat, char $\star$resp, dhsHandle dhsID);} \item[\sc description:] used by the NOCS and MSL to open a connection to the DHS. \item[\sc argument(s):] \begin{description} \item[\ ] \ \item[\emph{long $\star$istat}] the inherited status value. \item[\emph{char $\star$resp}] a user supplied buffer for message strings. \item[\emph{dhsHandle dhsID}] dhs handle. \end{description} \item[\sc return(s):] void. \item[\sc author(s):] Peter Ruckle, Phil Daly \item[\sc last modified:] \item[\sc license:] (c) 2004 AURA Inc. All rights reserved. Released under the GPL. \end{description}
\subsection {dhsUtilSysOpen} \begin{description} \item[\sc use:] \emph{void dhsUtilSysOpen(long $\star$istat, char $\star$resp, dhsHandle $\star$dhsID, ulong whoami);} \item[\sc description:] used by the NOCS and MSL to open a connection to the DHS. \item[\sc argument(s):] \begin{description} \item[\ ] \ \item[\emph{long $\star$istat}] the inherited status value. \item[\emph{char $\star$resp}] a user supplied buffer for message strings. \item[\emph{dhsHandle $\star$dhsID}] returned dhs handle. \item[\emph{ulong whoami}] identifier for NOCS or MSL or other system making the call. \end{description} \item[\sc return(s):] void. \item[\sc author(s):] Peter Ruckle, Phil Daly \item[\sc last modified:] \item[\sc license:] (c) 2004 AURA Inc. All rights reserved. Released under the GPL. \end{description}
